\Huge Literature Search Made Easy

### 2013-12-14 doc/article_1.tex
Added conclusion

\section*{Experiments}

\subsection*{Data Collection}
Data is crawled from the online archive website arXiv. In fields like mathematics and physics, almost all scientific papers are self-archived on the arXiv. Despite not peer reviewed, arXiv has its submissions reviewed (or even recategorized if off-topic) by moderators that are experts in their fields of research. In addition, submission dates on arXiv more accurately reflect when the research project was completed and paper drafted, since usually papers are posted on arXiv months before they are finally published on a peer reviewed journal or conference. Based on these facts, we believe arXiv is a better collection of research works than any journal or conference alone.\newline
The titles, authors, abstracts and citation of papers are scraped from API of \url{http://export.arxiv.org/api/} using Python and stored in separate files according to the publish year. We used only papers in condensed matter physics since one of us is familiar to the field, the methods demonstrated in this report however can be applied to the analysis any field. The corpus contains 14185 abstracts from year 1992 to 2003 and 4645 unique words and 11255 unique phrases after our data processing procedure.

@@

\section*{Conclusion}

>>>>

\section*{Evaluation}

\subsection*{Experiment Setup}
Data is crawled from the online archive website arXiv. In fields like mathematics and physics, almost all scientific papers are self-archived on the arXiv. Despite not peer reviewed, arXiv has its submissions reviewed (or even recategorized if off-topic) by moderators that are experts in their fields of research. In addition, submission dates on arXiv more accurately reflect when the research project was completed and paper drafted, since usually papers are posted on arXiv months before they are finally published on a peer reviewed journal or conference. Based on these facts, we believe arXiv is a better collection of research works than any journal or conference alone.\newline
The titles, authors, abstracts and citation of papers are scraped from API of \url{http://export.arxiv.org/api/} using Python and stored in separate files according to the publish year. We used only papers in condensed matter physics since one of us is familiar to the field, the methods demonstrated in this report however can be applied to the analysis any field. The corpus contains 14185 abstracts from year 1992 to 2003 and 4645 unique words and 11255 unique phrases after our data processing procedure.

@@

\section*{Conclusion}
In this work, we proposed a phrase-based extension to topic modeling which improves the clustering performance and enables effective interpretation of the document context. Phrases contain important information on the correlation between documents and can help human to understand since many words appear in combinations. The two-phase phrase extraction mechanism first enumerates word combinations and then filters out significant phrases based on cross document validation. This approach implicitly selects the key phrases in the corpus since it leverages the information hidden in multiple documents. In the evaluation, we compared three scenarios, i.e. word-only, phrase-only, and word+phrase. In both hLDA and DTM modeling, we can clearly see that with phrase information the result is much more accurate and easy to interpret.
